---
title: "The data"
description: >-
  The parts of the data package, the tables of the database, their codebooks, and three things to know before
  counting anything.
---

```{r}
#| label: setup
#| include: false
source("_common.R")
contracts <- arrow::read_parquet("sample/core/Contracts.parquet")
labels_sample <- arrow::read_parquet("sample/core/Labels.parquet")
comp <- sample_composition()
package_link <- link_or_gap(
  vars$data$package_link,  # the folder of the whole package, from _variables.yml
  "the whole package"      # what the reader sees
)
n_span_files <- length(list.files(
  "sample/spans",          # the span files of the sample
  pattern = "\\.parquet$"  # the codebook beside them is not a span file
))
```

The data package {{< var data.version >}} comes in `r nrow(parts)` parts: `r fmt_int(published_total("files"))` files
besides the checksum manifest, `r fmt_bytes(published_total("bytes"))` in all, the parts below and a README at the
root of the package. Each part is a folder that can be downloaded on its own. The parts are shared from
{{< var data.archive >}}, each with its own download link.`r doi_text(vars$data$archive_doi)`

Every example on this site reads the sample in `sample/` of the [site's repository]({{< var site.repository >}}). It
holds `r comp$labelled` contracts of the labelled sample, `r comp$per_category` from each of the `r comp$categories`
detailed categories, plus `r comp$rejected` attachments the text screen rejected and all `r comp$copy_rows` registrant
copies of `r comp$copy_attachments` attachments filed by several registrants, so that the checks below have something
to show: `r comp$rows` rows in all, with the rows every table and span file holds for them. To run an example, clone
the repository and run the code from its root. The examples need the R packages `arrow`, `dplyr`, `stringi` and
`tibble`; none needs the data package.

## The parts

```{r}
#| label: parts-sections
#| echo: false
#| results: asis
for (i in seq_len(nrow(parts))) {
  key <- parts$Part[i]
  bytes_key <- paste0(
    "folder.bytes.",  # the size of a part in package_numbers.csv
    key               # this part
  )
  files_key <- paste0(
    "folder.files.",  # the number of files of a part in package_numbers.csv
    key               # this part
  )
  cat(sprintf(
    "### %s {#part-%s}\n\n%s\n\n",  # heading, anchor, then the summary as the author wrote it
    parts$Title[i],                  # the part's title in data/parts.csv
    key,                             # a stable anchor for links from other pages
    parts$Summary[i]                 # the author's summary, unchanged
  ))
  cat(sprintf(
    "- %s in %s files\n- %s\n\n",  # size and file count, then the state of the part
    fmt_bytes(num(bytes_key)),     # read from package_numbers.csv, never typed
    fmt_int(num(files_key)),       # read from package_numbers.csv, never typed
    part_state(                    # published with its link, or the state in words
      parts$Status[i],  # published, request or planned
      parts$Link[i]     # a link only where the part is published
    )
  ))
}
```

## Getting a part

Each part above links to its own folder; `r package_link` has a link of its own. At the root of the package are a
`README.md` and a `MANIFEST.sha256`, which lists every file with its SHA-256 checksum. {{< var data.archive >}} may
deliver a large folder as several zip files; unpack them into one folder, with `MANIFEST.sha256` at its root, before
checking. From that folder (macOS, Linux), the first line checks the whole package and the second only the parts its
pattern names, here `core` and `spans`:

```bash
shasum -a 256 -c MANIFEST.sha256
grep -E '  (core|spans)/' MANIFEST.sha256 | shasum -a 256 -c
```

## Reading the files

The tables are parquet files. The package's README reads them as follows:

- R: `arrow::read_parquet("core/Contracts.parquet")`
- Python: `pandas.read_parquet("core/Contracts.parquet")`
- SQL: `duckdb -c "SELECT count(*) FROM 'core/Contracts.parquet'"`

No `.dta` files are published; [the Stata page](stata.qmd) says how to read the tables in Stata.

The sample keeps the package's folders, file names and columns, so an example moves to the package by replacing
`sample/` with the root of the package. The documents are the exception. The sample keeps them in one file,
`text/exhibit10/exhibit10_sample.parquet`, where the package has one file per type and filing year,
`text/<type>/<type>_<year>.parquet`. The sample holds Exhibit 10 attachments only, without the `HTML` column, the
document as retrieved from EDGAR. It carries no contract index, no models and no extraction image.

A file too large for memory is opened lazily and filtered before it is collected:

```{r}
#| label: read-lazy
exhibits <- arrow::open_dataset("sample/text/exhibit10")  # a folder of parquet files, opened as one table
wanted <- arrow::read_parquet(
  "sample/core/Contracts.parquet",  # the contracts table
  col_select = "DocID"              # only the key is needed here
)$DocID[1]                          # one document of the sample

exhibits |>
  dplyr::filter(DocID %in% wanted) |>  # the documents a study needs
  dplyr::select(
    DocID,  # the document
    YQ,     # its filing year and quarter
    DocExt  # its file type as filed
  ) |>
  dplyr::collect()  # the rows are read here
```

On the package the same code, with `sample/` removed, opens `text/exhibit10`: every filing year as one table.

## The tables of the core part

```{r}
#| label: core-helper
#| include: false
read_codebook <- function(file) {
  readr::read_csv(
    file,                                    # one codebook, from the folder it documents
    col_types = readr::cols(.default = "c")  # a codebook is text throughout
  ) |>
    dplyr::mutate(dplyr::across(
      dplyr::everything(),                          # every column may carry a wrapped line
      function(x) stringi::stri_replace_all_regex(  # each cell unwrapped
        x,       # the cell text
        "\\s+",  # a line break and its indent inside a cell
        " "      # read as the single space it stands for
      )
    ))
}
key_columns <- function(table, columns) {
  codebook_file <- sprintf(
    "sample/core/%s_Codebook.csv",  # the codebook of the table
    table                           # Contracts, Summaries, ...
  )
  wanted <- stringi::stri_split_regex(
    stringi::stri_trim_both(columns),  # the column names, separated by spaces or line breaks
    "\\s+"                             # one name per word
  )[[1]]
  read_codebook(codebook_file) |>
    dplyr::filter(Column %in% wanted) |>
    dplyr::select(
      Column,  # the column
      Meaning  # the codebook's meaning, unchanged
    ) |>
    knitr::kable()
}
summaries <- arrow::read_parquet("sample/core/Summaries.parquet")
places <- arrow::read_parquet("sample/core/Places.parquet")
termdocs <- arrow::read_parquet("sample/core/TermDocs.parquet")
cto_orders <- arrow::read_parquet("sample/core/CtoOrders.parquet")
```

The core part holds the tables below with their codebooks, the contract index, the labelled sample and the keyword
terms. The meanings shown are the codebook's own.

### Contracts

One row per registrant copy of an Exhibit 10 attachment: `r fmt_int(num("rows.contracts"))` rows, of which the
sample holds `r nrow(contracts)`. The filing, the classification and the content variables of the contract sit side
by side; below are its keys, the filing, the rejection and copy flags, the labels and the sample flags:

```{r}
#| label: core-contracts
#| echo: false
key_columns(
  "Contracts",  # the table
  "DocID HashDocument HashIndex CIK DateFiled FormType UrlDocument MultFiler PrimaryFiler Removed RemClass
   Class ClassRollup ClassBroad AmendType DescSample EstiSample"  # keys, copy to count, rejection, labels, samples
)
```

`EstiSample` marks the paper's estimation sample, which requires a Compustat match; Compustat is not published
([what needs WRDS](reproduce.qmd#what-needs-wrds)).

### Summaries

One row per current report (Form 8-K or 8-K/A) with an Item 1.01 text announcing a material agreement:
`r fmt_int(num("rows.summaries"))` rows. `SumAttached` is 1 where the filing carried an Exhibit 10 and 0 where the
agreement was announced without the contract. The sample holds the `r nrow(summaries)` announcements that carried a
sampled contract.

```{r}
#| label: core-summaries
#| echo: false
key_columns(
  "Summaries",                                                                       # the table
  "HashIndex DocID DateFiled SumAttached SumDates SumDateFirst SumLagDays SumWords SumBoiler"  # filing, timing, text
)
```

### Places

One row per contract, geographic level (country, state, county or city) with its state and country, party role and
law-clause flag, with the number of mentions: `r fmt_int(num("rows.places"))` rows, `r fmt_int(nrow(places))` in the
sample. The table does not name cities or counties; `spans/places_geo.parquet` (`GeoUnit`) names them. `GeoCountry`
keeps the country's name as found in the text, so one country can take several rows in a contract; count countries on
`GeoCountryIso`. Like TermDocs below, the table holds the primary copy of each attachment (`PrimaryFiler == 1`);
`HashDocument` reaches every registrant copy.

```{r}
#| label: core-places
#| echo: false
key_columns(
  "Places",                                                                          # the table
  "DocID HashDocument GeoLevel GeoState GeoCountryIso GeoCountry PartyRole InLawClause nMentions"  # place, whose, count
)
```

### TermDocs

One row per contract and term family, `r length(unique(termdocs$Family))` families, on the primary copy of the
contract: `r fmt_int(num("rows.termdocs"))` rows, `r fmt_int(nrow(termdocs))` in the sample. `HashDocument` reaches
the other registrant copies.

```{r}
#| label: core-termdocs
#| echo: false
key_columns(
  "TermDocs",                                              # the table
  "DocID HashDocument Family nHits nTerms HasTerm FirstPos PerKWords"   # the family, how strongly it is used
)
```

### CtoOrders

One row per exhibit reference in a confidential treatment order, whatever the order decided (`Status`) and whether
or not it was linked to a contract (`LinkStatus`): `r fmt_int(num("rows.ctoorders"))` rows. The sample holds the
`r nrow(cto_orders)` references linked to a sampled contract.

```{r}
#| label: core-ctoorders
#| echo: false
key_columns(
  "CtoOrders",                                                                       # the table
  "OrderDocID OrderDate Status IsExtension ExhibitNo ReleaseDate DocID LinkStatus"   # the order, its terms, its contract
)
```

### The contract index, the labelled sample and the keyword terms

`ContractIndex.csv.gz` locates each contract on EDGAR, keyed on `DocID`: the filing (`AccessionNumber`, `CIK`,
`CompanyName`, `FormType`, `DateFiled`), the attachment within it (`DocName`, `DocSeq`, `DocDesc`), its labels and
the two EDGAR links; [its codebook below](#contractindex) lists every column. It is a compressed CSV, so it opens
without a parquet reader.

`Labels.parquet` is the labelled sample: one row per labelled contract with the annotators' labels and the
cross-validation fold in which it was held out (`Fold`), `r fmt_int(num("rows.labels"))` rows, of which the sample
holds `r nrow(labels_sample)`.

`KeywordTerms.parquet` holds the keyword terms of all three classification tasks, `r fmt_int(num("rows.keywordterms"))`
rows, with `Task` naming the task a term belongs to. It is described with [the keyword classifier](methods.qmd#keywords).

## The codebooks

```{r}
#| label: codebook-helper
#| include: false
codebook_table <- function(file) {
  codebook <- read_codebook(file)
  shown <- c(
    "File",                                                  # the span file a row describes, where there is one
    "Column",                                                # the column
    "Type",                                                  # its type
    "Meaning",                                               # what it holds
    if (any(codebook$StataName != codebook$Column)) "StataName"  # its Stata name, only where one differs
  )
  codebook <- dplyr::select(
    codebook,             # one row per column of the table
    dplyr::any_of(shown)  # File exists in the span codebook only
  )
  table_name <- sub(
    "_Codebook\\.csv$",  # Contracts_Codebook.csv ...
    "",                  # ... becomes Contracts
    basename(file)       # the file name without its folder
  )
  element_id <- paste0(
    "codebook-",  # a prefix that cannot clash with the page's own ids
    table_name    # one id per codebook
  )
  meaning_column <- which(names(codebook) == "Meaning") - 1
  DT::datatable(
    codebook,                # one row per column of the table
    elementId = element_id,  # a fixed id, so that every render writes the same page
    rownames = FALSE,        # the row number carries no information
    options = list(          # the settings of the DataTables widget
      pageLength = 10,       # ten columns at a time keeps the page short
      columnDefs = list(list(            # one rule for one column
        className = "codebook-meaning",  # styles.css gives the meaning room to read
        targets = meaning_column         # DataTables counts columns from 0
      ))
    )
  )
}
codebook_files <- list.files(
  "sample",                      # the codebooks of the sample
  pattern = "_Codebook\\.csv$",  # one per table, one for the span files, one for the documents
  recursive = TRUE,              # they sit in core/, spans/ and text/
  full.names = TRUE              # read_csv needs the path
)
stata_names_kept <- all(vapply(
  codebook_files,                              # every codebook
  function(file) {
    codebook <- read_codebook(file)
    all(codebook$StataName == codebook$Column)  # TRUE where no column is renamed for Stata
  },
  logical(1)                                   # one answer per codebook
))
stata_sentence <- if (stata_names_kept) {
  "Every column keeps its name in Stata."
} else {
  "Where a column takes another name in Stata, its codebook below shows `StataName`."
}
```

Every table in `core/` has a codebook beside it (`*_Codebook.csv`), one row per column with its type and meaning. The
span files share one, whose `File` column names the file a row describes, and the documents in `text/` have their
own. The sample holds them where the package does. `r stata_sentence` The search box above each codebook filters its
rows.

### Contracts

```{r}
#| label: codebook-contracts
#| echo: false
codebook_table("sample/core/Contracts_Codebook.csv")
```

### Summaries

```{r}
#| label: codebook-summaries
#| echo: false
codebook_table("sample/core/Summaries_Codebook.csv")
```

### Places

```{r}
#| label: codebook-places
#| echo: false
codebook_table("sample/core/Places_Codebook.csv")
```

### TermDocs

```{r}
#| label: codebook-termdocs
#| echo: false
codebook_table("sample/core/TermDocs_Codebook.csv")
```

### CtoOrders

```{r}
#| label: codebook-ctoorders
#| echo: false
codebook_table("sample/core/CtoOrders_Codebook.csv")
```

### Labels

```{r}
#| label: codebook-labels
#| echo: false
codebook_table("sample/core/Labels_Codebook.csv")
```

### KeywordTerms

```{r}
#| label: codebook-keywordterms
#| echo: false
codebook_table("sample/core/KeywordTerms_Codebook.csv")
```

### ContractIndex

```{r}
#| label: codebook-contractindex
#| echo: false
codebook_table("sample/core/ContractIndex_Codebook.csv")
```

### Spans

One codebook covers the `r n_span_files` span files.

```{r}
#| label: codebook-spans
#| echo: false
codebook_table("sample/spans/Spans_Codebook.csv")
```

### Text

```{r}
#| label: codebook-text
#| echo: false
codebook_table("sample/text/Text_Codebook.csv")
```

## Three things to know before counting

The examples below start from the contracts table of the sample:

```{r}
#| label: read-contracts
contracts <- arrow::read_parquet("sample/core/Contracts.parquet")  # core/Contracts.parquet in the package
```

### The unit of observation is the registrant copy

One row of the contracts table is one registrant's copy of one Exhibit 10 attachment. When a filing names two
registrants, the same attachment arrives twice, once under each registrant's CIK. `HashDocument` identifies the
attachment itself and is shared by its copies; `DocID` identifies the copy. `DocID` is the registrant's CIK and the
hash of the attachment joined by a hyphen, as the check below confirms; the accession number sits in `UrlIndexPage`
and, under its own name, in the contract index.

```{r}
#| label: unit-docid
contracts |>
  dplyr::summarise(
    Rows = dplyr::n(),                              # copies in the sample
    Attachments = dplyr::n_distinct(HashDocument),  # distinct documents among them
    DocIDIsCikAndHash = all(  # TRUE when every key is the CIK and the hash, not the accession number
      DocID == paste(
        CIK,           # the registrant
        HashDocument,  # the attachment
        sep = "-"      # joined as in the published key
      )
    )
  )
```

The entity variables were computed once per attachment, on the copy marked `PrimaryFiler == 1`, and repeated on the
other copies. A statistic over contracts rather than over registrant copies therefore keeps only that copy:

```{r}
#| label: unit-primary
contracts |>
  dplyr::count(
    MultFiler,    # 1 where the filing names more than one registrant
    PrimaryFiler  # 1 on the copy the entity values were computed from
  )
```

The sample carries such copies, so the filter does something here:

```{r}
#| label: unit-filter
contracts_unique <- contracts |>
  dplyr::filter(PrimaryFiler == 1)

nrow(contracts_unique)
```

That is `r nrow(contracts) - nrow(contracts_unique)` of the `r nrow(contracts)` rows dropped as further copies of an
attachment already counted.

### Rejected attachments stay in the file

`Removed` marks an attachment that failed the screen for usable text, and `RemClass` gives the reason. These
attachments stay in the table, flagged, so that what was set aside remains visible; an analysis that wants readable
contracts filters on `Removed`.

```{r}
#| label: removed-count
contracts |>
  dplyr::count(
    Removed,  # TRUE where the attachment failed the screen for usable text
    RemClass  # why it was set aside
  )
```

The sample carries `r sum(contracts$Removed)` such attachments, so the count above gives their reasons and the filter
below drops them:

```{r}
#| label: removed-filter
contracts_readable <- contracts_unique |>
  dplyr::filter(!Removed)

nrow(contracts_readable)
```

The two filters together leave `r nrow(contracts_readable)` of the `r nrow(contracts)` rows of the sample: one
readable contract each.

### Span offsets are 0-based and half-open

Every span file locates its entity with a start and a stop offset into the published text of the document. The
offsets are 0-based and half-open, and they count characters, not bytes. In R the span is
`stringi::stri_sub(TextRaw, Start + 1, Stop)`; in Python it is `text[Start:Stop]`.

```{r}
#| label: spans-slice
options(arrow.use_altrep = FALSE)  # plain R strings, so a text joined to many spans is not converted for each
text <- arrow::read_parquet("sample/text/exhibit10/exhibit10_sample.parquet")
dates <- arrow::read_parquet("sample/spans/date_spans.parquet")

dates |>
  utils::head(8) |>
  dplyr::inner_join(
    text,         # the published text the offsets point into
    by = "DocID"  # a span file and the text share the document key
  ) |>
  dplyr::transmute(
    DocID,                       # the document
    DateStart,                   # 0-based start
    DateStop,                    # half-open stop
    Sliced = stringi::stri_sub(  # what the offsets cut out of the text
      TextRaw,                   # the published text of the document
      DateStart + 1,             # a 0-based start is R's 1-based first character
      DateStop                   # a half-open stop is R's inclusive last character
    ),
    DateText                     # what the span file stores
  )
```

The same holds for every span file. Each names its offsets after its entity (`DateStart`, `MentionStart`, ...) and
most store the text they found beside them; the governing-law file stores none.

```{r}
#| label: spans-check
offset_check <- function(file) {
  spans <- arrow::read_parquet(file) |>
    dplyr::inner_join(
      text,         # the published text the offsets point into
      by = "DocID"  # a span file and the text share the document key
    )
  start <- grep(
    "Start$",      # the first ...Start column is the span's own start
    names(spans),  # the columns of this span file
    value = TRUE   # the name rather than its position
  )[1]
  end <- sub(
    "Start$",  # DateStart, MentionStart, ...
    "Stop",    # ... pair with DateStop, MentionStop, ...
    start      # the start column found above
  )
  stored <- grep(
    "Text$",       # DateText, PlaceText, SpanText, ...: the text the extractor stored
    names(spans),  # the columns of this span file
    value = TRUE   # the name rather than its position
  )[1]
  sliced <- stringi::stri_sub(
    spans$TextRaw,       # the published text of each span's document
    spans[[start]] + 1,  # 0-based start to R's 1-based first character
    spans[[end]]         # half-open stop is R's inclusive last character
  )
  tibble::tibble(
    File = basename(file),                    # the span file
    Rows = nrow(spans),                       # rows in the sample
    WithOffsets = sum(!is.na(sliced)),        # rows that locate a span
    Stored = stored,                          # the column holding the stored text, if any
    SliceEqualsStored = if (is.na(stored)) {  # spans whose slice is the stored text
      NA_integer_
    } else {
      sum(
        sliced == spans[[stored]],  # slice and stored text agree
        na.rm = TRUE                # a row without offsets has nothing to compare
      )
    }
  )
}

list.files(
  "sample/spans",           # every span file of the sample
  pattern = "\\.parquet$",  # the codebook beside them is not a span file
  full.names = TRUE         # read_parquet needs the path, not the name
) |>
  lapply(offset_check) |>
  dplyr::bind_rows()
```

A rule that reads a document's spans in text order sorts them first, for instance with
`dplyr::arrange(DocID, DateStart)`.

A contract without any identified organisation has one row in `org_mentions` without a span: a placeholder with
`PartyRole` and `MatchKind` `none`. The same contracts have `HasNoParty == 1` in the contracts table:

```{r}
#| label: spans-noparty
no_party <- arrow::read_parquet("sample/spans/org_mentions.parquet") |>
  dplyr::filter(is.na(MentionStart))

no_party |>
  dplyr::select(
    DocID,      # the document without an organisation
    PartyRole,  # none: no party was found
    MatchKind   # none: nothing was matched
  ) |>
  dplyr::left_join(
    dplyr::select(  # the flag from the contracts table
      contracts,    # one row per contract
      DocID,        # the same document in the contracts table
      HasNoParty    # 1 where the extractor found no organisation
    ),
    by = "DocID"  # one row per document
  )
```

The flag records what the extractor returned, not what the contract says:

```{r}
#| label: spans-noparty-text
named <- text |>
  dplyr::filter(DocID %in% no_party$DocID) |>
  dplyr::transmute(
    DocID,                                             # the document without an organisation mention
    NamedCompany = stringi::stri_extract_first_regex(  # the company the text names
      TextRaw,                                                    # the published text
      "[A-Z][\\w&.]*(?: [A-Z][\\w&.]*)*, a Delaware corporation"  # a name followed by its incorporation
    )
  )

named
```

`r sum(!is.na(named$NamedCompany))` of these `r nrow(named)` documents name a company in their text all the same.

Counting characters matters. Curly quotes, section signs and bullets take more than one byte each, and a tool that
slices bytes cuts the wrong text for every span after the first of them:

```{r}
#| label: spans-bytes
first_wide <- text |>
  dplyr::transmute(
    DocID,                                         # the document
    FirstWide = stringi::stri_locate_first_regex(  # where byte and character positions first part
      TextRaw,                                     # the published text
      "[^\\u0000-\\u007f]"                         # the first character outside ASCII
    )[, "start"]
  )

dates |>
  dplyr::left_join(
    first_wide,   # each document's first character outside ASCII
    by = "DocID"  # one position per document
  ) |>
  dplyr::summarise(
    Spans = dplyr::n(),        # date spans in the sample
    AfterWideCharacter = sum(  # spans a tool that slices bytes would cut wrongly
      DateStart >= FirstWide,  # the span starts after a character of more than one byte
      na.rm = TRUE             # a document without such a character shifts nothing
    )
  )
```

`r sum(!is.na(first_wide$FirstWide))` of the `r nrow(text)` documents in the sample contain such a character.

In Python the slice is the same once the text is a `str`. `PlaceStart` and `LawStart` are stored as doubles, and
pandas reads the offsets of `org_mentions` as floats because its rows without a span have none; dropping those rows
and casting with `int()` makes the block work on every span file:

```python
import pandas as pd

text = pd.read_parquet("sample/text/exhibit10/exhibit10_sample.parquet").set_index("DocID")["TextRaw"]
dates = pd.read_parquet("sample/spans/date_spans.parquet").dropna(subset=["DateStart"])

dates["Sliced"] = [
    text[doc][int(start):int(stop)]  # 0-based and half-open: Python's own slice
    for doc, start, stop in zip(
        dates["DocID"],       # the document
        dates["DateStart"],   # 0-based start
        dates["DateStop"],    # half-open stop
    )
]
```

## Known issues

The package's README describes these issues of {{< var data.version >}}; the figures come from the sample.

```{r}
#| label: issue-columbia
#| echo: false
places_geo <- arrow::read_parquet("sample/spans/places_geo.parquet")
columbia <- places_geo |>
  dplyr::filter(
    GeoCountryIso == "COL",   # coded as Colombia, the country
    PlaceText == "Columbia"   # from the word Columbia, which is not it
  )
usa_spellings <- places |>
  dplyr::filter(GeoCountryIso == "USA") |>
  dplyr::distinct(GeoCountry) |>
  dplyr::arrange(GeoCountry) |>
  dplyr::pull(GeoCountry)
usa_text <- paste0(
  "\"",            # each spelling in quotation marks
  usa_spellings,   # the names the Places table of the sample gives the United States
  "\"",            # closing the quotation
  collapse = ", "  # one list
)
```

- **Columbia.** The gazetteer reads "Columbia" as the country Colombia, so Colombia is heavily over-counted in
  `Places`, `places_geo` and the country counts of `Contracts`; in US contracts the word is almost always the
  District of Columbia, British Columbia or a US city. In the sample, `r nrow(columbia)` rows of `places_geo` read
  "Columbia" as Colombia.
- **Country spellings.** A country can appear under several names, some in other languages; count on
  `GeoCountryIso`. In the Places table of the sample, `USA` appears as `r usa_text`.
- **Durations.** `DurationYears` is left missing above 30 years (`DurationDropped` says so); other date columns are
  not capped.
- **Broad label.** The paper's broad category is `ClassRollup`. `ClassBroad` comes from an additional model trained
  on the broad labels directly; `HierConsistent` marks where the two differ
  ([classification](methods.qmd#classification)).
- **Span offsets.** `LawStart` and `PlaceStart` are stored as whole-numbered doubles, the other offsets as integers.
- **Parties.** A contract without any identified organisation has one row in `org_mentions` without a span
  ([above](#span-offsets-are-0-based-and-half-open)).
- **No document-level gold set** exists for the entities. The labelled sample in `Labels.parquet` covers the
  classification, not the extraction.
- **The text as read.** `TextRaw` is exactly the text the classifiers and extractors read. In some HTML documents,
  quotation marks, apostrophes and dashes appear as control characters (U+0080 to U+009F): they were written in
  Windows-1252 and read as Latin-1. The package's README gives a repair in R and in Python that swaps one character
  for one, so every offset stays valid. A model or extractor run on repaired text reads slightly different input from
  the one that produced the data.

### Not in the package

- **Compustat.** It is licensed. `EstiSample` marks the rows of the paper's estimation sample; the match to
  Compustat can be rebuilt from `CIK` and `DateFiled` ([what needs WRDS](reproduce.qmd#what-needs-wrds)).
- **Amounts.** Monetary amounts were extracted but are not used by the paper and are not published.

## Licences

The tables, the span files and the other data of the package are published under {{< var data.licence >}}. The
fine-tuned classifiers are published under {{< var data.licence_models >}}, the licence of the model they were
trained from. The documents in [the documents part](#part-text) are filings the SEC made public on EDGAR. The
extraction image contains LexNLP, which is licensed under the AGPL-3.0, and carries a notice
(`lexnlp/NOTICE.md`). The full texts of the licences are in the `LICENSES` folder of the
[site's repository]({{< var site.repository >}}).
