---
title: "The analysis of material contracts"
subtitle: "Data and methods"
---

```{r}
#| label: setup
#| include: false
source("_common.R")
composition <- sample_composition()
if (length(composition$per_category) != 1) {
  stop("The sample no longer draws the same number of labelled contracts from each category")
}
contracts_codebook <- readr::read_csv(
  "sample/core/Contracts_Codebook.csv",    # the package's own codebook, which lists the paper's sample selection
  col_types = readr::cols(.default = "c")  # every column as text
)
paper_years <- stringi::stri_match_first_regex(
  contracts_codebook$Meaning[contracts_codebook$Column == "SampleStepDesc"],  # the selection steps in words
  "outside ([0-9]{4})-([0-9]{4})"                                             # the filing years the sample keeps
)
if (nrow(paper_years) != 1 || anyNA(paper_years)) {
  stop("The Contracts codebook no longer names the filing years of the paper's sample in SampleStepDesc")
}
```

This site publishes the data and the methods of the paper below. The data package holds the material contracts, Exhibit
10 to a filing, that registrants filed with the SEC with forms 10-K, 10-Q, 8-K, 20-F, S-1, S-4, F-1 and F-4 and their
amendments between {{< var data.first_year >}} and {{< var data.last_year >}}: `r fmt_int(num("rows.contracts"))`
registrant copies of these attachments, classified by type, with the parties, places, law clauses, dates, terms
and redactions extracted from their text, and the documents themselves. The paper's sample starts in
`r paper_years[1, 2]`.

## Four ways in

- **[Data](data.qmd).** What each part of the data package holds, the tables and their columns, and three things to
  know before counting anything.
- **[Methods](methods.qmd).** How the contracts were classified and their entities extracted, and how to turn the
  published spans into variables of your own, each with an example on the sample.
- **[Stata](stata.qmd).** Where the paper's Stata code will be published, what it needs, and how to read the tables
  and slice a span in Stata.
- **[Code](reproduce.qmd).** Where the code that built the database is, and what needs a WRDS subscription.

Every R example on this site runs, from the root of a clone of the [site's repository]({{< var site.repository >}}),
on the sample in its `sample/` folder: `r composition$per_category` labelled contracts from each of the
`r composition$categories` detailed categories, `r composition$rejected` rejected attachments and all
`r composition$copy_rows` registrant copies of `r composition$copy_attachments` attachments whose filing names several
registrants.

## The parts of the data package

```{r}
#| label: parts-overview
#| echo: false
bytes_keys <- paste0(
  "folder.bytes.",  # the size of a part in package_numbers.csv
  parts$Part        # one key per part
)
files_keys <- paste0(
  "folder.files.",  # the number of files of a part in package_numbers.csv
  parts$Part        # one key per part
)
tibble::tibble(
  Part = sprintf(              # the part, linked to its section on the data page
    "[%s](data.qmd#part-%s)",  # the section of the part on the data page
    parts$Title,               # as data/parts.csv names it
    parts$Part                 # the anchor of that section
  ),
  Size = fmt_bytes(vapply(  # what the download costs
    bytes_keys,             # read, never typed
    num,                    # one figure from package_numbers.csv
    numeric(1)              # one figure per part
  )),
  Files = vapply(  # how many files the part holds
    files_keys,    # read, never typed
    num,           # one figure from package_numbers.csv
    numeric(1)     # one figure per part
  ),
  Status = part_state(  # whether it can be downloaded yet
    parts$Status,       # published, request or planned
    parts$Link          # a link only where the part is published
  )
) |>
  knitr::kable()
```

The package is version {{< var data.version >}}: `r fmt_bytes(published_total("bytes"))` in
`r fmt_int(published_total("files"))` files, the parts above and a README at the root, beside a checksum manifest. The
parts are shared from {{< var data.archive >}}, each with its own download link;
[getting a part](data.qmd#getting-a-part) says how to check a download.

## The paper and how to cite it

{{< var paper.authors >}}. {{< var paper.title >}} ({{< var paper.status >}}).`r doi_text(vars$paper$doi)`

Please cite the paper, and the data package with its version, {{< var data.version >}}.`r doi_text(vars$data$archive_doi)`
The tables and span files are licensed under {{< var data.licence >}} and the classifiers
under {{< var data.licence_models >}}; [the data page](data.qmd#licences) says what applies to the documents and the
extraction image. Questions and requests to remove material go to {{< var site.contact >}}.
