---
title: "The analysis of material contracts"
subtitle: "Data and methods"
---

```{r}
#| label: setup
#| include: false
source("_common.R")
composition <- sample_composition()
if (length(composition$per_category) != 1) {
  stop("The sample no longer draws the same number of labelled contracts from each category")
}
contracts_codebook <- readr::read_csv(
  "sample/core/Contracts_Codebook.csv",    # the package's own codebook, which lists the paper's sample selection
  col_types = readr::cols(.default = "c")  # every column as text
)
paper_years <- stringi::stri_match_first_regex(
  contracts_codebook$Meaning[contracts_codebook$Column == "SampleStepDesc"],  # the selection steps in words
  "outside ([0-9]{4})-([0-9]{4})"                                             # the filing years the sample keeps
)
if (nrow(paper_years) != 1 || anyNA(paper_years)) {
  stop("The Contracts codebook no longer names the filing years of the paper's sample in SampleStepDesc")
}
```

This site documents the data and the methods of the paper cited below. The data package holds the material
contracts filed with the SEC as Exhibit 10 to forms 10-K, 10-Q, 8-K, 20-F, S-1, S-4, F-1 and F-4 and their amendments
between {{< var data.first_year >}} and {{< var data.last_year >}}: `r fmt_int(num("rows.contracts"))` registrant
copies of these attachments, each classified by contract type, with the parties, places, law clauses, dates, terms
and redactions extracted from the text, and the documents themselves. The paper's sample starts in
`r paper_years[1, 2]`.

## What is on this site

- **[Data](data.qmd).** The parts of the data package, the tables and their columns, and the conventions of the
  tables.
- **[Methods](methods.qmd).** How the contracts were classified and their entities extracted, how to apply the
  published classifiers and the extraction image, and how to turn the published spans into variables. Each method
  comes with an example on the sample.
- **[Stata](stata.qmd).** Where the paper's Stata code will be published and what it needs.
- **[Code](reproduce.qmd).** Where the code that built the database is, and what needs a WRDS subscription.

Every R example on this site runs on the sample in the [`sample/` folder]({{< var site.sample >}}) of the site's
repository, from the root of a clone of that repository: `r composition$per_category` labelled contracts from each of
the `r composition$categories` detailed categories, `r composition$rejected` rejected attachments and all
`r composition$copy_rows` registrant copies of `r composition$copy_attachments` attachments whose filing names
several registrants.

## The parts of the data package

```{r}
#| label: parts-overview
#| echo: false
bytes_keys <- paste0(
  "folder.bytes.",  # the size of a part in package_numbers.csv
  parts$Part        # one key per part
)
files_keys <- paste0(
  "folder.files.",  # the number of files of a part in package_numbers.csv
  parts$Part        # one key per part
)
tibble::tibble(
  Part = sprintf(              # the part, linked to its section on the data page
    "[%s](data.qmd#part-%s)",  # the section of the part on the data page
    parts$Title,               # as data/parts.csv names it
    parts$Part                 # the anchor of that section
  ),
  Size = fmt_bytes(vapply(  # what the download costs
    bytes_keys,             # read, never typed
    num,                    # one figure from package_numbers.csv
    numeric(1)              # one figure per part
  )),
  Files = vapply(  # how many files the part holds
    files_keys,    # read, never typed
    num,           # one figure from package_numbers.csv
    numeric(1)     # one figure per part
  ),
  Status = part_state(  # whether it can be downloaded yet
    parts$Status,       # published, request or planned
    parts$Link          # a link only where the part is published
  )
) |>
  knitr::kable()
```

The package is version {{< var data.version >}}: `r fmt_bytes(published_total("bytes"))` in
`r fmt_int(published_total("files"))` files. Each part is a folder with its own download link on
{{< var data.archive >}}; a README and a checksum manifest sit at the root of the package
([checking a download](data.qmd#checking-a-download)).

## The paper and how to cite it

{{< var paper.authors >}}. {{< var paper.title >}} ({{< var paper.status >}}).`r doi_text(vars$paper$doi)`

Please cite the paper, and the data package with its version, {{< var data.version >}}.`r doi_text(vars$data$archive_doi)`
The tables and span files are licensed under {{< var data.licence >}} and the classifiers
under {{< var data.licence_models >}}; [the data page](data.qmd#licences) says what applies to the documents and the
extraction image. Questions and requests to remove material go to {{< var site.contact >}}.
