---
title: "The methods"
description: >-
  How the contracts were classified and their entities extracted, how to apply the published classifiers and the
  extraction image, and how to turn the published spans into variables. Each method comes with an example on the
  sample.
---

```{r}
#| label: setup
#| include: false
source("_common.R")
comp <- sample_composition()
n_broad <- dplyr::n_distinct(arrow::read_parquet("sample/core/Labels.parquet")$ClassBroad)
n_span_files <- length(list.files(
  "sample/spans",          # the span files of the sample
  pattern = "\\.parquet$"  # the codebook beside them is not a span file
))

# The terms the amendment lexicon lists for Original. The page says the amendment rule never uses them, so the
# render stops if a published keyword label was decided by one.
keyword_setup <- arrow::read_parquet("sample/core/KeywordTerms.parquet")
original_terms <- keyword_setup$Term[
  keyword_setup$Task == "AmendType" &  # the amendment task
    keyword_setup$Class == "Original"  # the terms that point to an original
]
if (any(arrow::read_parquet("sample/core/Contracts.parquet")$KwAmendTypeTerm %in% original_terms)) {
  stop("A KwAmendTypeTerm of the sample is an Original term; the keyword section misdescribes the rule")
}
```

Every example on this page reads the sample in the [`sample/` folder]({{< var site.sample >}}) of the site's
repository: `r comp$rows` rows of the contracts table. Of these, `r comp$labelled` are labelled contracts,
`r comp$per_category` from each of the `r comp$categories` detailed categories; `r comp$rejected` are attachments the
text screen rejected; and `r comp$copy_rows` are the registrant copies of `r comp$copy_attachments` attachments whose
filing names more than one registrant. The sample illustrates the file structure; it is not representative of the
corpus.

## Classification {#classification}

Each contract carries three labels, each from a fine-tuned Legal-BERT model (`nlpaueb/legal-bert-base-uncased`) of
its own: a detailed category out of `r comp$categories`, a broad category out of `r n_broad`, and whether the
document is an original contract or an amendment. A model reads the first 256 or the first 512 tokens of a document
and ignores the rest. Each task was trained at both lengths, which makes the `r num("models.count")` models of
[the classifiers part](data.qmd#part-models).

The paper's contract type is `Class`, the detailed category from the model `ClassDetailed_L256`, and its broad type
is `ClassRollup`, the roll-up of `Class` to the broad categories. `ClassBroad` comes from an additional model
trained on the broad labels directly; where it differs from the roll-up, `HierConsistent` is `FALSE`.

Cross-validation over five folds of the labelled contracts selected a configuration for each task; for the broad
task it selected the 512-token model. The published labels come from the 256-token models in all three tasks.

The detailed categories and the broad category each rolls up to, as the contracts table publishes them:

```{r}
#| label: class-taxonomy
contracts <- arrow::read_parquet("sample/core/Contracts.parquet")

contracts |>
  dplyr::distinct(
    ClassRollup,  # the broad parent the paper uses
    Class         # the detailed category under it
  ) |>
  dplyr::arrange(
    ClassRollup,  # parents in alphabetical order
    Class         # and their children below them
  )
```

### Worked example {#classification-example}

The published labels sit in the contracts table; the reference labels of the labelled contracts sit in the labelled
sample. The labels were given with [rLabelDocs]({{< var code.rlabeldocs >}}), a Shiny application for labelling
documents, and `LabelRound` records the labelling round, `Round1` or `Round2` (Online Appendix C of the paper).

```{r}
#| label: class-read
labels <- arrow::read_parquet("sample/core/Labels.parquet")
labelled <- contracts |>
  dplyr::filter(DocID %in% labels$DocID)
```

The published detailed categories of the labelled contracts. The reference labels put `r comp$per_category` of them
in each category, so a count away from `r comp$per_category` is a document the detailed model placed elsewhere:

```{r}
#| label: class-distribution
labelled |>
  dplyr::count(Class)
```

The roll-up the paper uses is published beside the detailed label, as `ClassRollup`; it does not have to be rebuilt
from a map. Against the broad model's own label, on every row of the sample:

```{r}
#| label: class-rollup
contracts |>
  dplyr::count(
    ClassRollup,  # the broad category as the paper uses it, rolled up from Class
    ClassBroad    # the label of the model trained on the broad labels
  )
```

The two agree except on `r sum(!contracts$HierConsistent)` of the `r nrow(contracts)` rows, which are the rows where
`HierConsistent` is `FALSE`:

```{r}
#| label: class-hierconsistent
contracts |>
  dplyr::count(
    HierConsistent,                    # FALSE where the broad model departs from the roll-up
    Agree = ClassRollup == ClassBroad  # the comparison the flag stands for
  )
```

The published labels against the reference labels, task by task and by labelling round:

```{r}
#| label: class-agreement
compared <- labels |>
  dplyr::select(
    DocID,                          # the document
    LabelDetailed = ClassDetailed,  # the reference detailed category
    LabelBroad = ClassBroad,        # the reference broad category
    LabelAmend = AmendType,         # the reference original or amendment
    LabelRound                      # the labelling round
  ) |>
  dplyr::inner_join(
    contracts,    # the published labels
    by = "DocID"  # one row per labelled contract in both
  )

compared |>
  dplyr::summarise(
    Documents = dplyr::n(),                     # documents compared
    Detailed = sum(Class == LabelDetailed),     # agreement on the detailed categories
    RollUp = sum(ClassRollup == LabelBroad),    # the paper's broad label against the reference
    BroadModel = sum(ClassBroad == LabelBroad), # the separate broad model against the same reference
    Amendment = sum(AmendType == LabelAmend),   # agreement on original against amendment
    .by = LabelRound                            # Round1 or Round2
  )
```

The labelled contracts on which `Class` or `ClassRollup` departs from the reference label:

```{r}
#| label: class-disagreement
compared |>
  dplyr::filter(Class != LabelDetailed | ClassRollup != LabelBroad) |>
  dplyr::select(
    DocID,                  # the document
    LabelDetailed,          # the reference label
    Class,                  # what the detailed model chose
    BertClassDetailedProb,  # how sure it was
    LabelBroad,             # the reference broad category
    ClassRollup,            # the paper's broad label, rolled up from Class
    ClassBroad,             # what the separate broad model chose
    HierConsistent          # FALSE where that model departs from the roll-up
  )
```

Read this agreement as a check that the files fit together, not as accuracy. The labelled sample is the training data
of the published models: every document above was among those they were fitted on. Accuracy on documents a model has
not seen comes from the cross-validation over the folds, not from this comparison.

On the `r sum(!compared$HierConsistent)` labelled contracts where `HierConsistent` is `FALSE`, the detailed model
agrees with the reference label in `r sum(!compared$HierConsistent & compared$Class == compared$LabelDetailed)`.

### Applying a classifier {#applying-a-classifier}

[The classifiers part](data.qmd#part-models) holds the `r num("models.count")` models as zip archives, one per task
and context length. All start from Legal-BERT and were trained on the `r fmt_int(num("rows.labels"))` labelled
contracts in `core/Labels.parquet`.

| Archive | Task | Categories | Context | Labelled the published data |
|:--|:--|--:|--:|:--|
| `ClassDetailed_L256.zip` | Contract type (`Class`) | `r comp$categories` | 256 tokens | yes |
| `ClassDetailed_L512.zip` | Contract type | `r comp$categories` | 512 tokens | no |
| `ClassBroad_L256.zip` | Broad type from a separate model (`ClassBroad`) | `r n_broad` | 256 tokens | yes |
| `ClassBroad_L512.zip` | Broad type from a separate model | `r n_broad` | 512 tokens | no |
| `AmendType_L256.zip` | Original or amendment (`AmendType`) | 2 | 256 tokens | yes |
| `AmendType_L512.zip` | Original or amendment | 2 | 512 tokens | no |

Beside the archives, `models_index.csv` maps each archive to the folder it unpacks to, and `deployed.parquet` records
the configuration cross-validation selected for each task, with its macro-F1. `README.md` in the same folder is the
usage guide; this section repeats it.

**What an archive holds.** Each archive unpacks to one folder named after the training run; the name spells out the
context length (`L`), epochs (`E`), batch size (`B`), learning rate (`LR`), class weights (`W1` on, `W0` off) and
seed (`S`). Inside it:

```
<Task>__nlpaueb-legal-bert-base-uncased__TText_L<len>_E<epochs>_B32_LR<rate>_W<weights>_S42__FINAL/
  model/            the model: config.json with the label mapping (id2label), the weights
                    (model.safetensors) and the tokenizer (tokenizer.json, vocab.txt, ...)
  config.json       the training run: data, labels, hyperparameters, software versions
  train_log.parquet the training loss per epoch
  run.log           the run's log
```

**Running a model.** The models were trained with Python 3.12, PyTorch 2.10 and transformers 4.49; recent versions
of both libraries load them. A GPU helps but is not needed.

```bash
pip install torch transformers pandas pyarrow
unzip ClassDetailed_L256.zip
```

```python
import pandas as pd
import torch
from transformers import AutoModelForSequenceClassification, AutoTokenizer

model_dir = "ClassDetailed__nlpaueb-legal-bert-base-uncased__TText_L256_E6_B32_LR2e-05_W1_S42__FINAL/model"
max_len = 256                      # the context length the model was trained with: L256 or L512

tok = AutoTokenizer.from_pretrained(model_dir)
model = AutoModelForSequenceClassification.from_pretrained(model_dir).eval()
id2label = {int(k): v for k, v in model.config.id2label.items()}

docs = pd.read_parquet("text/exhibit10/exhibit10_2012.parquet", columns=["DocID", "TextRaw"]).head(32)
enc = tok(docs["TextRaw"].fillna("").tolist(), truncation=True, max_length=max_len,
          padding="max_length", return_tensors="pt")
with torch.inference_mode():
    probs = torch.softmax(model(**enc).logits, dim=-1)
top = probs.topk(2, dim=-1)

docs["Label"] = [id2label[i] for i in top.indices[:, 0].tolist()]
docs["Prob"] = top.values[:, 0].tolist()
docs["Label2"] = [id2label[i] for i in top.indices[:, 1].tolist()]
docs["Prob2"] = top.values[:, 1].tolist()
```

**Three rules the published labels follow.** Your own use should follow them too:

- The input is `TextRaw` from [the documents part](data.qmd#part-text), the document's full text, unchanged.
- The model reads the first `max_len` tokens and ignores the rest (`truncation=True`). Use the length in the
  archive's name; a 256-token model given 512 tokens is not the model that was scored.
- The label mapping travels with the model (`id2label` in `model/config.json`); never rebuild it from a list of
  category names.

`Label`, `Prob`, `Label2` and `Prob2` correspond to `BertClassDetailed`, `BertClassDetailedProb`,
`BertClassDetailed2` and `BertClassDetailed2Prob` in the contracts table, and likewise for the other two tasks. The
documents part holds exactly the text the models read, so a 256-token model run on it reproduces those columns, up
to the last digits of a probability that differ between processors.

**Rolling up.** To roll a detailed label up to the broad category the paper uses (`ClassRollup`): take the part
before the colon, with `Customer / Supplier` and `R&D` rolling up to `Purchases and Sales`, and `Leases`, `Licenses`
and `Other` standing alone. The taxonomy table above shows every pair.

The models are derived from Legal-BERT, published under {{< var data.licence_models >}}, and are published under the
same licence.

## The keyword classifier {#keywords}

Beside each transformer label the contracts table carries a label from a keyword classifier, an independent second
instrument. The core part publishes its lexicon as `KeywordTerms.parquet`:
`r fmt_int(num("rows.keywordterms"))` rows, one per task, category and term, with `Task` naming the task
(`ClassDetailed`, `ClassBroad` or `AmendType`). `Term` is the keyword, one to three lower-case words searched in the
first 256 words of a document. `Precision` is the share of the labelled documents containing it that belong to its
category, and `Power`, the term's strength, is the lower bound of the Wilson interval of that precision. The codebook
lists the other columns.

The package publishes the terms and the labels they gave; the code that finds a term in a text is in the pipeline
(see [the Code page](reproduce.qmd)). In the contracts table the keyword label of the detailed task is
`KwClassDetailed`, with the keyword that decided it in `KwClassDetailedTerm` and its `Power` in
`KwClassDetailedPower`; the label is missing where no keyword applied or two categories tied. The broad task has the
same three columns. `ClassDetailedFlag` and `ClassBroadFlag` say whether the keyword label confirmed the transformer,
contradicted it, or left it unchecked by giving no category. For the amendment task `KwAmendType` is `Amended` where
an amendment term applies and `Original` otherwise. The lexicon also lists `r length(original_terms)` terms for
`Original`, which that rule does not use.

### Worked example {#keyword-example}

Every row the keyword classifier labelled in the detailed or broad task records the term that decided the label.
The terms behind one category:

```{r}
#| label: keyword-terms
contracts |>
  dplyr::filter(KwClassDetailed == "Leases") |>
  dplyr::count(
    KwClassDetailedTerm,   # the term that decided the label
    KwClassDetailedPower,  # its Power in the lexicon
    name = "Rows"          # how many rows of the sample it labelled
  ) |>
  dplyr::arrange(dplyr::desc(KwClassDetailedPower))
```

The lexicon itself is in the sample, so the same terms can be read with their `Power` and `Precision`. The strongest
terms of that category, by rank:

```{r}
#| label: keyword-lexicon
keyword_terms <- arrow::read_parquet("sample/core/KeywordTerms.parquet")

keyword_terms |>
  dplyr::filter(
    Task == "ClassDetailed",  # the detailed task
    Class == "Leases"         # the category the terms above decided
  ) |>
  dplyr::arrange(Rank) |>
  dplyr::select(
    Rank,       # position within the category, by Power
    Term,       # the keyword itself
    Power,      # the lower bound of the Wilson interval of its precision
    Precision,  # the share of its labelled documents that are Leases
    HitsTot     # labelled documents containing it
  ) |>
  utils::head(10)
```

The same file holds the other two tasks under their own `Task` value:

```{r}
#| label: keyword-tasks
keyword_terms |>
  dplyr::count(
    Task,            # the three tasks share one file
    name = "Terms"   # terms published for each
  )
```

How often the keyword classifier gives a label at all, and whether it agrees with the transformer when it does:

```{r}
#| label: keyword-flags
contracts |>
  dplyr::count(ClassDetailedFlag)
```

`contradicted` is a disagreement between two instruments, not yet an error of either. On the labelled contracts the
reference labels say which one was right, bearing in mind that both instruments were built from these documents:

```{r}
#| label: keyword-contradicted
compared |>
  dplyr::filter(ClassDetailedFlag == "contradicted") |>
  dplyr::count(
    TransformerRight = Class == LabelDetailed,        # the transformer's label matches the reference label
    LexiconRight = KwClassDetailed == LabelDetailed   # the lexicon's label matches the reference label
  )
```

## Extraction {#extraction}

The organisation candidates come from LexNLP 2.3.0, run inside the container image of
[the extraction image part](data.qmd#part-lexnlp); places, dates, law clauses and redaction markers come from the
pipeline's own extractors. Rules written in R, part of the pipeline, decide which candidates become spans: they
match organisations to the registrant and give each party a role, attach places to parties, read the jurisdiction a
law clause names, and place each date relative to the filing date.
[Running the extraction image](#running-the-extraction-image) says how to apply the image to documents of your own.

| Span file | One row per |
|:--|:--|
| `org_mentions` | mention of a party; one row without a span for a contract with none |
| `places_geo` | place named, attached to a party or not |
| `law_clauses` | law clause |
| `date_spans` | date that could be read |
| `term_spans` | stated period, or a clause stating the contract has no fixed length |
| `redact_spans` | redaction or omission marker |

Beside each span the files keep what the rules read: whether a place was attached to a party, whether a date falls
before or after the filing, whether a period is left open, whether a marker withholds text.
[From spans to variables](#spans-to-variables) turns one span file into a column of the contracts table.

### The span files of the sample

Each span file holds one row per entity found, keyed on the document and located by its offsets into the text (see
[the data page](data.qmd#span-offsets-are-0-based-and-half-open)). Counted per document:

```{r}
#| label: spans-read
span_files <- list.files(
  "sample/spans",           # every span file of the sample
  pattern = "\\.parquet$",  # the codebook beside them is not a span file
  full.names = TRUE         # read_parquet needs the path, not the name
)
names(span_files) <- sub(
  "\\.parquet$",        # the file extension
  "",                   # dropped, so the name is the kind of span
  basename(span_files)  # the file names without their folder
)
spans <- lapply(
  span_files,          # one path per kind of span
  arrow::read_parquet  # each file read whole: the sample is small
)
```

```{r}
#| label: spans-per-document
per_document <- function(kind) {
  start <- grep(
    "Start$",              # the first ...Start column is the span's own start
    names(spans[[kind]]),  # the columns of this span file
    value = TRUE           # the name rather than its position
  )[1]
  spans[[kind]] |>
    dplyr::filter(!is.na(.data[[start]])) |>
    dplyr::count(
      DocID,         # one count per document
      name = "Rows"  # the rows of this kind in the document
    ) |>
    dplyr::summarise(
      Kind = kind,                   # the span file
      Documents = dplyr::n(),        # documents with at least one span
      Spans = sum(Rows),             # spans in all
      Median = stats::median(Rows),  # spans in the typical document
      Max = max(Rows)                # spans in the busiest document
    )
}

names(spans) |>
  lapply(per_document) |>
  dplyr::bind_rows()
```

The spans of one contract, kind by kind: the shortest contract of the sample that appears in all `r n_span_files`
span files.

```{r}
#| label: spans-example-contract
text <- arrow::read_parquet("sample/text/exhibit10/exhibit10_sample.parquet")
with_all_kinds <- Reduce(
  intersect,  # documents present in every span file
  lapply(     # one vector of document keys per span file
    spans,               # every span file
    function(x) x$DocID  # the documents it holds
  )
)
example_doc <- text |>
  dplyr::filter(DocID %in% with_all_kinds) |>
  dplyr::slice_min(stringi::stri_length(TextRaw)) |>
  dplyr::pull(DocID)
```

```{r}
#| label: spans-example-row
#| include: false
example_row <- contracts |>
  dplyr::filter(DocID == example_doc)
```

It was filed by `r example_row$CompanyName` on `r example_row$DateFiled` and described by the filer as
`r example_row$DocDesc`; its `DocID` is `r example_doc`. The spans of one kind, in the order they appear in the text:

```{r}
#| label: spans-one-kind
spans_of <- function(kind) {
  start <- grep(
    "Start$",              # the first ...Start column is the span's own start
    names(spans[[kind]]),  # the columns of this span file
    value = TRUE           # the name rather than its position
  )[1]
  spans[[kind]] |>
    dplyr::filter(DocID == example_doc) |>
    dplyr::arrange(.data[[start]]) |>
    dplyr::select(-DocID)
}

spans_of("term_spans")
```

Every kind of span in the same contract, one tab each:

```{r}
#| label: spans-tabset
#| echo: false
#| results: asis
cat("::: {.panel-tabset}\n\n")
for (kind in names(spans)) {
  cat(sprintf(
    "#### %s\n\n::: {.table-scroll}\n\n",  # one tab per kind, its table in a box that scrolls sideways
    kind                                   # named after the span file
  ))
  print(knitr::kable(spans_of(kind)))
  cat("\n:::\n\n")
}
cat(":::\n")
```

### Running the extraction image {#running-the-extraction-image}

`contracts-lexnlp-17a366b025fe.tar.gz` in [the extraction image part](data.qmd#part-lexnlp) is the Docker image that
extracted the organisation candidates of the database: LexNLP 2.3.0 in Python 3.8, with the NLTK data it needs
baked in, so it runs offline. The rules that turn candidates into the published parties are part of the pipeline,
not of the image. `README.md` beside the image is the usage guide; this section repeats it.

**Loading it.**

```bash
docker load -i contracts-lexnlp-17a366b025fe.tar.gz     # restores the image as contracts-lexnlp:latest
```

The image is built for 64-bit ARM (`linux/arm64`, native on Apple Silicon). On an Intel or AMD machine Docker runs
it under emulation, which works but is several times slower. To run natively there, rebuild it from the `Dockerfile`
in the pipeline repository ([material-contracts]({{< var code.pipeline >}}), folder `contracts-lexnlp/`, at commit
`e3f97216ef96d58d6001faf23bc2e5017eed5b7a`) and pin its packages to the `requirements.lock.txt` published beside the
image; a rebuild is the same software, not the same image.

**Running it.** The image reads parquet files with a `DocID` and a `TextRaw` column, which is what
[the documents part](data.qmd#part-text) holds, and writes one parquet file with one row per match:

```bash
docker run --rm -v "$PWD":/work contracts-lexnlp:latest \
  exhibit10_2012.parquet \
  --output lexnlp_org_2012.parquet \
  --label ORG \
  --n-process 8
```

| Option | Default | Meaning |
|:--|:--|:--|
| inputs | | one or more parquet files or folders, relative to the mounted directory |
| `--output` | | the parquet file to write |
| `--label` | `ORG` | what to extract: `ORG`, `DATE`, `GPE`, `MONEY`, `AMOUNT`, `PERCENT`, `RATIO`, `DURATION` |
| `--id-col`, `--text-col` | `DocID`, `TextRaw` | the input columns |
| `--timeout` | 60 | seconds per extractor and document; past it, the document keeps its other rows |
| `--max-chars` | 0 (off) | read only the first N characters of each document |
| `--n-process` | 1 | worker processes; 0 or less uses all cores |

The output has `DocID`, `Start`, `Stop`, `Span`, `Label`, `LabelRaw`, `Engine` and `Model`, plus columns specific to
each label (for `ORG`: `Name`, `NameAbbr`, `TypeFull`, `TypeAbbr`, `TypeLabel`, `Description`). Offsets follow the
same rule as the published spans: `TextRaw[Start:Stop] == Span`. A document without any match appears once, with
empty offsets, so every input document is accounted for.

The database used the image for `ORG` only; its places, dates, law clauses and redaction markers come from the
pipeline's own extractors. The documents part holds exactly the text the image read. The wrapper that runs LexNLP is
inside the image at `/app/extract_lexnlp.py` and in the pipeline repository in `contracts-lexnlp/` at the commit
above.

LexNLP is licensed under the GNU Affero General Public License v3.0 (see `lexnlp/NOTICE.md` in the part). The image
contains it and is distributed under that licence.

## From spans to variables {#spans-to-variables}

`TermYears` in the contracts table is the longest term the contract states, in years. A contract can state several
periods, and `term_spans` keeps every one of them, with the period in years (`TermYears`), the phrasing that matched
(`TermKind`) and whether the clause states the contract has no fixed length (`IsOpen`). The periods with a length:

```{r}
#| label: term-candidates
terms <- arrow::read_parquet("sample/spans/term_spans.parquet")

candidates <- terms |>
  dplyr::filter(
    !is.na(TermYears),  # the phrase parsed into a length
    !IsOpen             # an open-ended period has no length to compare
  )

candidates |>
  dplyr::count(
    TermKind,           # the phrase the period came from
    name = "Spans"      # candidates of that kind in the sample
  )
```

The published rule, recomputed from the spans: the longest of these periods in each contract, against the published
column.

```{r}
#| label: term-rule
per_contract <- candidates |>
  dplyr::summarise(
    LongestStated = max(TermYears),  # the published rule
    Candidates = dplyr::n(),         # periods to choose among
    .by = DocID                      # one value per contract
  ) |>
  dplyr::inner_join(
    dplyr::select(  # the published column beside the recomputed one
      contracts,    # one row per contract
      DocID,        # the contract
      TermYears     # the published term in years
    ),
    by = "DocID"  # the span files are keyed on the same document
  ) |>
  dplyr::filter(!is.na(TermYears))  # contracts for which a term was published

term_check <- per_contract |>
  dplyr::summarise(
    Contracts = dplyr::n(),                   # contracts with a candidate period
    SeveralCandidates = sum(Candidates > 1),  # contracts that state more than one period
    PublishedRuleMatches = sum(dplyr::near(   # contracts the recomputed rule reproduces
      LongestStated,  # the published rule, recomputed
      TermYears       # the published column
    ))
  )

term_check
```

The recomputed rule gives the published value in `r term_check$PublishedRuleMatches` of the
`r term_check$Contracts` contracts, and `r term_check$SeveralCandidates` of them state more than one period. What the
chosen period governs:

```{r}
#| label: term-period-kind
candidates |>
  dplyr::arrange(TermStart) |>
  dplyr::slice_max(
    TermYears,          # the published rule: the longest period
    n = 1,              # one period per contract
    with_ties = FALSE,  # of periods equally long, the first the text states
    by = DocID          # per contract
  ) |>
  dplyr::count(
    PeriodKind,          # what the chosen period governs
    name = "Contracts"   # contracts whose longest period is of that kind
  )
```

The published column is one rule over the spans. `PeriodKind` records what each period governs, from the word
before it; its codebook adds: "Descriptive only; no variable uses it." A study that wants the agreement's own term
rather than the longest stated period filters on it and writes its rule in a line.

The span files are keyed on the primary copy of each attachment; `HashDocument` in the contracts table reaches the
other registrant copies.
